---
title: "Conversion_EDA"
author: "Regan Yee"
date: "February 28, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)

## Setup data source
setwd("~/Documents/Data Science Challenges/Conversion Rate/")
data = read.csv("./conversion_data.csv")
```

## Data Summaries

```{r summaries}
## Examine the first row of the data
head(data,1)
## Gets the summary of the data
summary(data)
```

```{r}
## Let's factorize and re-level some boolean variables
data$new_user = as.factor(data$new_user)
levels(data$new_user) = c("No", "Yes")

data$converted = as.factor(data$converted)
levels(data$converted) = c("No", "Yes")
```

Let's examine how many new users there were:

``` {r counts, echo=FALSE}
data %>% group_by(new_user) %>% summarize(count=n()) %>% 
  ggplot(aes(x=new_user, y=count)) +
  geom_bar(stat="identity") +
  xlab("New User?") + 
  ylab("Count") +
  ggtitle("Count of New Users in Dataset") +
  geom_text(aes(label=count, vjust=-.35))
```

And how many people actually converted in this dataset?

```{r echo=FALSE}
data %>% group_by(converted) %>% summarize(count=n()) %>%
  ggplot(aes(x=converted, y=count)) +
  geom_bar(stat="identity") +
  xlab("Converted?") + 
  ylab("Count") +
  ggtitle("Conversions in Dataset") +
  geom_text(aes(label=count, vjust=-.35))
```

Visually inspecting the sources data:

``` {r, echo=FALSE}
data %>% group_by(source) %>% summarize(count=n()) %>% 
  arrange(-count) %>% 
  mutate(source = factor(source, source)) %>% 
  ggplot(aes(x=source, y=count)) + 
  geom_bar(stat="identity") +
  xlab("Source") + 
  ylab("Count") +
  ggtitle("Count of Sources in Dataset") +
  geom_text(aes(label=count, vjust=-.35))
```

Visually inspecting the pages visited data:

``` {r, echo=FALSE}
data %>% group_by(total_pages_visited) %>% summarize(count=n()) %>% 
  ggplot(aes(x=total_pages_visited, y=count)) + 
  geom_bar(stat="identity") +
  xlab("Pages Visited") + 
  ylab("Count") +
  ggtitle("Number of Pages Visited by Users")
```

Let's look at the age breakdown of the users on the site:

``` {r, echo=FALSE}
## Let's create an age range factor
data$bins = cut(data$age, breaks=c(0,11,17,24,34,44,54,64,max(data$age)))
levels(data$bins) = c("0-11", "12-17", "18-24", "25-34", "35-44", "45-54", "55-64", "65+")

data %>% group_by(bins) %>% summarize(count=n()) %>% 
  ggplot(aes(x=bins, y=count)) +
  geom_bar(stat="identity") +
  xlab("Age") + 
  ylab("Count") +
  ggtitle("Age Breakdown of Dataset") +
  geom_text(aes(label=count, vjust=-.35))
```


## Insights
* The current conversion rate in the dataset is **3.23%**
* We can see that a majority of the users are from the US.
* The age data has some data that needs to be validated as there is a user with age of 123 (very unlikely!)
* 49% of users are coming in via SEO; 28% of users via ads, and the remaining 23% are direct users.
* On average, a user will view 5 pages in a visit
* 68% of the users are creating new accounts

## Questions
Let's look at a couple of questions:

1. Where are most of the conversions coming from? By source, by country?
2. What is the typical age of a converter?
3. What is the correlation between the factors in the dataset?

## Conversion Metrics
```{r}
data %>% 
  filter(converted=="Yes") %>% 
  group_by(source) %>% 
  summarize(count=n())

data %>% 
  filter(converted=="Yes") %>% 
  group_by(country) %>% 
  summarize(count=n())

data %>% 
  filter(converted=="Yes") %>% 
  group_by(bins) %>% 
  summarize(count=n())

data %>% 
  filter(converted=="Yes") %>% 
  group_by(total_pages_visited) %>% 
  summarize(count=n()) %>% 
  ggplot(aes(x=total_pages_visited, y=count)) + 
  geom_bar(stat="identity") +
  xlab("Pages Visited") + 
  ylab("Count") +
  ggtitle("Number of Pages Visited by Converted Users")
```
